\chapter*{Marking Scheme}
\addcontentsline{toc}{chapter}{Marking Scheme}

This document is structured to address all marking criteria for the Software Engineering G6046 group coursework. The table below outlines each requirement, the maximum marks available, and where evidence of meeting that requirement can be found within this report.

\vspace{1cm}

\begin{center}
\begin{tabular}{|p{3.2cm}|p{1.5cm}|p{5.8cm}|p{2.2cm}|}
\hline
\rowcolor{darkblue}
\textcolor{white}{\textbf{Element}} &
\textcolor{white}{\textbf{Marks}} &
\textcolor{white}{\textbf{Description}} &
\textcolor{white}{\textbf{Link}} \\
\hline

Planning Docs & 5 & Project plan, PERT/Gantt charts, risk analysis & \hyperref[chap:planning]{\color{blue}\underline{Chapter \ref*{chap:planning}}} \\
\hline

Planning --- Meeting Notes & 5 & Meeting records, action tracking, team decisions & \hyperref[sect:meeting]{\color{blue}\underline{Section \ref*{sect:meeting}}} \\
\hline

Process Documentation & 10 & Sprint documentation, user stories, Agile evidence & \hyperref[chap:process]{\color{blue}\underline{Chapter \ref*{chap:process}}} \\
\hline

Design Documentation: High Level & 5 & System architecture, component roles, interactions & \hyperref[chap:design-high]{\color{blue}\underline{Chapter \ref*{chap:design-high}}} \\
\hline

Design Documentation: Low Level & 5 & Class diagrams, OO principles, API design & \hyperref[chap:design-low]{\color{blue}\underline{Chapter \ref*{chap:design-low}}} \\
\hline

Software Documentation & 5 & Code comments, XML DocStrings, IntelliSense cross-refs & \hyperref[chap:software]{\color{blue}\underline{Chapter \ref*{chap:software}}} \\
\hline

Testing Documentation & 10 & Unit tests, system tests, requirements traceability, edge cases & \hyperref[chap:process]{\color{blue}\underline{Chapter \ref*{chap:process}}} \\
\hline

Group Report & 5 & Achievements, issues, critical analysis, team organisation & \hyperref[chap:project-overview]{\color{blue}\underline{Chapter \ref*{chap:project-overview}}} \\
\hline

Code & 50 & Working game, AI player, GUI, customisation & Submitted codebase \\
\hline

\end{tabular}
\end{center}

\vspace{1em}

Known gaps against the highest marking bands. The following features are yet to be implemented and would strengthen the project if implemented.

\begin{itemize}
    \item Testing (9 to 10 band): Sprint 4 system tests (S4.1 to S4.12) were not fully executed before submission, so the Actual Result and Pass/Fail columns remain incomplete (Section~\ref{sec:sprint4}). Edge-case tests were performed for board movement (Sprint 3) but are not formally catalogued as a dedicated edge-case suite. Unit tests are linked to classes but not formally cross-referenced back to individual design artefacts (class diagram entries or sequence diagrams).
    \item Code (41 to 50 band): The AI player uses BFS-directed navigation toward envelope-candidate rooms and knowledge-filtered suggestions, but full notebook-based card-elimination deduction was not implemented (Section~\ref{sec:sprint4-known-issues}). Player names are not customisable, although the board design is. Watson Games specifically identified customisation as a selling point. The game does not feature animated character movement or formally verified cross-platform (Mac and PC) operation.
\end{itemize}

\newpage
